Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-13 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 Both the Scan Statistics proposed by Kulldorff, the Global Moran's I and the *LISA* were already used before in studies about spatial and spatio-temporal characteristics of Sars-CoV-2, the Scan Statistic for instance was already used once in studies about the spatio-temporal behavior of Covid-19 in the state of Sergipe in Brazil, while both the Global and Local Moran's I were used in chinese studies regarding the spatial characteristics of the pandemic in China, here these methods showed themselves to be useful while studying the spatial and spatio-temporal characteristics of the virus.

>>>>

 Both the Poisson Scan Statistic proposed by Kulldorff, the Global Moran's I and the *LISA* were already used before in studies about spatial and spatio-temporal characteristics of Sars-CoV-2, the Scan Statistic for instance was used once in studies about the spatio-temporal behavior of Covid-19 in the state of Sergipe in Brazil, while both the Global and Local Moran's I were used in chinese studies regarding the spatial characteristics of the pandemic in China, here these methods showed themselves to be useful while studying the spatial and spatio-temporal characteristics of the virus.
